Cyclone: Replication Middleware for NVM Clusters

### 2016-09-11 paper/paper.tex
More text in paper.

\subsection{Zero Copy Replication}
Consensus protcols such as RAFT usually have a simple common case path. Once a
quorum leader is elected, the leader's primary job is to transmit new entries
appended to the log to its followers. The primary job of a follower is to
receive these entries, append them to its log and send acknowledgments to the
leader. An entry is considered committed when the leader receives an
acknowledgment for an entry from a majority of the quorum. Followers receive
intimation of committed entries as piggybacked information on subsequent
replication messages.

>>>>

\subsection{Zero Copy Replication}
Consensus protcols such as RAFT usually have a simple common case path. Once a
quorum leader is elected, the leader's primary job is to transmit new entries
appended to its persistent log to its followers. The primary job of a follower
is to receive these entries, append them to its persistent log and send
acknowledgments to the leader. An entry is considered committed when the leader
receives an acknowledgment for an entry from a majority of the quorum. Followers
receive intimation of committed entries as piggybacked information on subsequent
replication messages.

In order to avoid copying the incoming RPC call to a persistent memory range,
Cyclone uses persistent memory on the system itself to allocate space for packet
buffers. However although a packet is accessible at the core the most up to date
data for the memory region occupied by the packet is in the CPU cache and not
necessarily in memory. To ensure that packet data has truly been made
persistent, Cyclone issues a series of cacheline flushes. This ensures that the
packet data is persistent. Cyclone maintains its log as a circular sequence of
pointers to packet buffers and therefore the append operation is completed by
adding a pointer to the received packet and flushing the cacheline containing
the pointer.
